\textbf{{\Large {Recursive algorithms, branching coefficients and applications}}}

### 2010-05-31 AffineLieAlgebras/InformalNotes/article.tex
pdf regen
Some changes
Minor changes

\pagenumbering{arabic}
\title{\textbf{{\Large {Recursive algorithms, branching coefficients and applications}}}}
\author{Vladimir Lyakhovsky \thanks{ Supported by
 RFFI grant N 09-01-00504 and the National Project RNP.2.1.1./1575 }\\
Theoretical Department, SPb State University,\\
198904, Sankt-Petersburg, Russia \\
e-mail:lyakh1507@nm.ru \\
[5mm] Anton Nazarov \thanks{ Supported by
the National Project RNP.2.1.1./1575 }\\
Theoretical Department, SPb State University,\\
198904, Sankt-Petersburg, Russia \\
e-mail:antonnaz@gmail.com
}
\maketitle

@@

It is important that the projection of some of positive roots of
the algebra $\mathfrak{g}$ can be equal to zero. These roots are orthogonal to the
root space of the subalgebra $\mathfrak{a}$ embedded into the root space of the
algebra $\mathfrak{g}$. Let's denote the subset of such roots by $\Delta^{+}_{\bot}
=\left\{\alpha\in\Delta_{\mathfrak{g}}^{+}:
\forall \beta\in \Delta_{\mathfrak{a}}^{+},\; \alpha\bot\beta \right\}$.

@@

It contains the following steps:
\begin{enumerate}
\item Construct the sets $\Delta^{+}$ and $\Delta_{\mathfrak{a}}^{+}$ of positive roots for the algebras $\mathfrak{a} \subset \mathfrak{g}$.
\item Select the positive roots $\alpha\in \Delta^{+}$ which are orthogonal to the root subspace of $\mathfrak{a}$ and form the set $\Delta^{+}_{\bot}$.
\item Construct the set $\Gamma$ \eqref{fan-defined}.
\item Construct the set $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights of the $\mathfrak{g}$-module $L^{(\mu)}$.
\item Select the weights $\left\{ \lambda=\omega(\mu+\rho) | \pi_{\mathfrak{a}_{\bot}}\lambda \in \bar{C}_{\mathfrak{a}_{\bot}} \right\}$ Since we have constructed the set $\Delta^{+}_{\bot}$ we can easily check wether the weight $\pi_{\mathfrak{a}_{\bot}}\lambda$ lies in the main Weyl chamber of $\mathfrak{a}_{\bot}$ by computing the scalar product of $\lambda$ with the roots of $\Delta^{+}_{\bot}$, it must be non-negative.
\item For $\lambda=\omega(\mu+\rho),\; \pi_{\mathfrak{a}_{\bot}}\lambda\in \bar{C}_{\mathfrak{a}_{\bot}}$ calculate the dimensions of the corresponding modules $\mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)$ using the Weyl formula with the set $\Delta^{+}_{\bot}$.
\item Calculate the anomalous branching coefficients in the main Weyl
  chamber of the subalgebra $\mathfrak{a}$ using the recurrent relation (\ref{recurrent-relation}).
\end{enumerate}

@@

\subsection{Affine Lie algebras}
\label{sec:affine-lie-algebras}
\subsubsection{Affine into affine embedding}
\label{sec:embedd-affine-algebr}

@@

Using the definition (\ref{fan-defined}) we get the fan $\Gamma_{\hat{A_1} \longrightarrow  \hat{B_2} }$ with the corresponding values $s(\gamma+\gamma_0)$(see the Figure \ref{fig:AffineB2A1Fan}).
Here we restricted the computation to the twelfth grade.
\begin{figure}[ph]
  \centering
  \includegraphics[width=130mm]{AffineB2_A1_fan.pdf}
  \caption{Fan for $\hat{A_1}\subset \hat{B_2}$}
  \label{fig:AffineB2A1Fan}
\end{figure}

@@

Performing the next step of the algorithm \ref{sec:algorithm} we project the anomalous weights to the weight space of the subalgebra $\hat{A_1}$ and find the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
The result of this computation up to the twelfth grade is presented in the Figure
\ref{fig:AffineB2_A1_anom_proj}.
\begin{figure}[h!tb]
  \centering
  \includegraphics[width=150mm]{AffineB2_A1_proj_anom.pdf}
  \caption{Projected anomalous weights and the dimensions of $\mathfrak{a}_{\bot}$-modules.}
  \label{fig:AffineB2_A1_anom_proj}
\end{figure}

@@

\begin{figure}[ph]
  \centering
  \includegraphics[width=130mm]{AffineB2_A1_branching.pdf}
  \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{B_2}$}
  \label{fig:AffineB2_A1_branching}
\end{figure}

@@

\section{Applications to the conformal field theory}
\label{sec:phys-appl}

@@

The set of the anomalous weights of this representation  is depicted in the Figure \ref{fig:affine_A2_anom_point} up to the sixth grade. We also show the root subspace of the subalgebra $\hat{A}_1$ under consideration as the dotted diagonal plane.

@@

Using the definition (\ref{fan-defined})  we construct ``the fan'' $\Gamma_{\hat A_1\to\hat A_2}$  with the corresponding values of the function $s(\gamma+\gamma_0)$ (see the Figure \ref{fig:AffineA2A1Fan}). 
Here we restricted the calculations to the first eight grades.
\begin{figure}[p]
  \centering
  \includegraphics[width=130mm]{AffineA2_A1_fan.pdf}
  \caption{The fan $\Gamma_{\hat{A_1}\subset \hat{A_2}}$}
  \label{fig:AffineA2A1Fan}
\end{figure}

The next step is to project the anomalous weights to $P_{\aht A_1}$.
The result up to the twelfth grade is presented in the Figure \ref{fig:AffineA2_A1_anom_proj}
\begin{figure}[h!tb]
  \centering
  \includegraphics[width=150mm]{AffineA2_A1_proj_anom.pdf}
  \caption{Projected anomalous weights and the dimensions of $\mathfrak{a}_{\bot}$-modules.}
  \label{fig:AffineA2_A1_anom_proj}
\end{figure}

Using the recurrent relation for the anomalous branching coefficients we get the result presented in Figure \ref{fig:AffineA2_A1_branching}. 
\begin{figure}[ph]
  \centering
  \includegraphics[width=110mm]{AffineA2_A1_branching.pdf}
  \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{A_2}$}
  \label{fig:AffineA2_A1_branching}
\end{figure}

We see that inside the main Weyl chamber of $\hat{A}_1$, which is dotted at the Figure \ref{fig:AffineA2_A1_branching}, there are only two non-zero anomalous weights. These are the branching coefficients. So the finite reducibility theorem holds and we get the decomposition
\begin{equation}
  \label{eq:43}
  L^{(0,0;1;0)}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{(0;4;0)}\oplus L_{\hat{A_1}}^{(4;4;0)}.
\end{equation}

@@

\begin{figure}[t]
  \begin{multicols}{2}
    \hfill
    \includegraphics[width=50mm]{A_1+A_1_to_A3.pdf}
    \hfill
    \caption{Representation for the special embedding  $su(2)\oplus su(2)\subset su(4)$}
    \label{fig:A_1+A_1_to_A3}
    \hfill
    \includegraphics[width=50mm]{A1+A1-A3.pdf}
    \hfill
    \caption{Embedded roots for the special embedding  $su(2)\oplus su(2)\subset su(4)$}
    \label{fig:A1+A1-A3}
  \end{multicols}
\end{figure}

>>>>

\pagenumbering{arabic}
\title{\textbf{{\Large {Recursive algorithms, branching coefficients and applications}}}}
\author{Vladimir Lyakhovsky \thanks{ Supported by
 RFFI grant N 09-01-00504 and the National Project RNP.2.1.1./1575 }\\
Theoretical Department, SPb State University,\\
198904, Sankt-Petersburg, Russia \\
e-mail:lyakh1507@nm.ru \\
[5mm] Anton Nazarov \thanks{ Supported by
the National Project RNP.2.1.1./1575 }\\
Theoretical Department, SPb State University,\\
198904, Sankt-Petersburg, Russia \\
e-mail:antonnaz@gmail.com
}
%\maketitle

@@

It is important that the ion of some of positive roots of
the algebra $\mathfrak{g}$ can be equal to zero. These roots are orthogonal to the
root space of the subalgebra $\mathfrak{a}$ embedded into the root space of the
algebra $\mathfrak{g}$. Let's denote the subset of such roots by $\Delta^{+}_{\bot}
=\left\{\alpha\in\Delta_{\mathfrak{g}}^{+}:
\forall \beta\in \Delta_{\mathfrak{a}}^{+},\; \alpha\bot\beta \right\}$.

@@

It contains the following steps:
\begin{enumerate}
\item Construct the sets $\Delta^{+}$ and $\Delta_{\mathfrak{a}}^{+}$ of positive roots for the algebras $\mathfrak{a} \subset \mathfrak{g}$.
\item Select the positive roots $\alpha\in \Delta^{+}$ which are orthogonal to the root subspace of $\mathfrak{a}$ and form the set $\Delta^{+}_{\bot}$.
\item Construct the set $\Gamma$ \eqref{fan-defined}.
\item Construct the set $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights of the $\mathfrak{g}$-module $L^{(\mu)}$.
\item Select the weights $\left\{ \lambda=\omega(\mu+\rho) | \pi_{\mathfrak{a}_{\bot}}\lambda \in \bar{C}_{\mathfrak{a}_{\bot}} \right\}$ Since we have constructed the set $\Delta^{+}_{\bot}$ we can easily check wether the weight $\pi_{\mathfrak{a}_{\bot}}\lambda$ lies in the main Weyl chamber of $\mathfrak{a}_{\bot}$ by computing the scalar product of $\lambda$ with the roots of $\Delta^{+}_{\bot}$, it must be non-negative.
\item For $\lambda=\omega(\mu+\rho),\; \pi_{\mathfrak{a}_{\bot}}\lambda\in \bar{C}_{\mathfrak{a}_{\bot}}$ calculate the dimensions of the corresponding modules $\mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)$ using the Weyl formula with the set $\Delta^{+}_{\bot}$.
\item Calculate the anomalous branching coefficients in the main Weyl
  chamber $\bar{C_{\mathfrak{a}}}$ of the subalgebra $\mathfrak{a}$ using the recurrent relation (\ref{recurrent-relation}).
\end{enumerate}

@@

\subsection{Affine into affine embedding}
\label{sec:embedd-affine-algebr}

@@

Using the definition (\ref{fan-defined}) we get the fan $\Gamma_{\hat{A_1} \longrightarrow  \hat{B_2} }$ with the corresponding values $s(\gamma+\gamma_0)$(see the Figure \ref{fig:AffineB2A1Fan}).
Here we restricted the computation to the twelfth grade.
\begin{figure}[h!tb]
  \centering
  \includegraphics[width=130mm]{AffineB2_A1_fan.pdf}
  \caption{The fan for $\hat{A_1}\subset \hat{B_2}$}
  \label{fig:AffineB2A1Fan}
\end{figure}

@@

Performing the next step of the algorithm \ref{sec:algorithm} we project the anomalous weights to the weight space of the subalgebra $\hat{A_1}$ and find the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
The result of this computation up to the twelfth grade is presented in the Figure
\ref{fig:AffineB2_A1_anom_proj}.
\begin{figure}[p]
  \centering
  \includegraphics[width=120mm]{AffineB2_A1_proj_anom.pdf}
  \caption{The projected anomalous weights and the dimensions of $\mathfrak{a}_{\bot}$-modules.}
  \label{fig:AffineB2_A1_anom_proj}
\end{figure}

@@

\begin{figure}[p]
  \centering
  \includegraphics[width=120mm]{AffineB2_A1_branching.pdf}
  \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{B_2}$}
  \label{fig:AffineB2_A1_branching}
\end{figure}

@@

%\newpage
\section{Applications to the conformal field theory}
\label{sec:phys-appl}

@@

The set $\widehat{\Psi^{(\omega_0)}}$  is depicted in the Figure \ref{fig:affine_A2_anom_point} up to the sixth grade. We also show the root subspace of the subalgebra $\hat{A}_1$ under consideration as the dotted diagonal plane.

@@

Using the definition (\ref{fan-defined})  we construct ``the fan'' $\Gamma_{\hat A_1\to\hat A_2}$  with the corresponding values of the function $s(\gamma+\gamma_0)$ (see the Figure \ref{fig:AffineA2A1Fan}). 
Here we restricted the calculations to the first eight grades.
\begin{figure}[h!tb]
  \centering
  \includegraphics[width=130mm]{AffineA2_A1_fan.pdf}
  \caption{The fan $\Gamma_{\hat{A_1}\subset \hat{A_2}}$}
  \label{fig:AffineA2A1Fan}
\end{figure}

The next step is to project the anomalous weights to $P_{\hat A_1}$.
The result up to the twelfth grade is presented in the Figure \ref{fig:AffineA2_A1_anom_proj}
\begin{figure}[h!tb]
  \centering
  \includegraphics[width=150mm]{AffineA2_A1_proj_anom.pdf}
  \caption{Projected anomalous weights and the dimensions of $\mathfrak{a}_{\bot}$-modules.}
  \label{fig:AffineA2_A1_anom_proj}
\end{figure}

Using the recurrent relation for the anomalous branching coefficients we get the result presented in Figure \ref{fig:AffineA2_A1_branching}. 
\begin{figure}[h!tb]
  \centering
  \includegraphics[width=110mm]{AffineA2_A1_branching.pdf}
  \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{A_2}$}
  \label{fig:AffineA2_A1_branching}
\end{figure}

We see that inside $\bar{C}_{\hat{A}_1}$, which is shown at the Figure \ref{fig:AffineA2_A1_branching}, there are only two non-zero anomalous weights. These are the branching coefficients. So the finite reducibility theorem holds and we get the decomposition
\begin{equation}
  \label{eq:43}
  L^{(0,0;1;0)}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{(0;4;0)}\oplus L_{\hat{A_1}}^{(4;4;0)}.
\end{equation}

@@

\begin{figure}[h!tb]
  \begin{multicols}{2}
    \hfill
    \includegraphics[width=50mm]{A_1+A_1_to_A3.pdf}
    \hfill
    \caption{Representation for the special embedding  $su(2)\oplus su(2)\subset su(4)$}
    \label{fig:A_1+A_1_to_A3}
    \hfill
    \includegraphics[width=50mm]{A1+A1-A3.pdf}
    \hfill
    \caption{Embedded roots for the special embedding  $su(2)\oplus su(2)\subset su(4)$}
    \label{fig:A1+A1-A3}
  \end{multicols}
\end{figure}
